Towards a Wide-Coverage Grammar

### 2013-06-24 slides/presentation.tex
Frame numbers
Moved multiple constraints to annex
Descriptions for schema examples

\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Outline}
    \tableofcontents[currentsection]
  \end{frame}
}

@@

\frame{\titlepage}

@@

  \begin{columns}[c]
    \begin{column}{0.5\textwidth}
      \begin{center}
        \includegraphics[height=0.7\textheight]{../diagrams/fail1.pdf}
      \end{center}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{center}
        \includegraphics[height=0.7\textheight]{../diagrams/fail2.pdf}
      \end{center}
    \end{column}
  \end{columns}
\end{frame}

  Combined:
  \begin{small}
  \begin{align*}
      C_{aime_1} &: NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}F} \limp NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}F} \limp S\_\textcolor{darkgreen}{EXT{=}NO} \\
      C_{aime_2} &: NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}T} \limp NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}F} \limp S\_\textcolor{darkgreen}{EXT{=}ROOT} \\
      C_{aime_3} &: NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}F} \limp NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}T} \limp S\_\textcolor{darkgreen}{EXT{=}ROOT} \\
      C_{aime_4} &: NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}F} \limp NP\_\textcolor{darkgold}{NUM{=}PL}\_\textcolor{darkgreen}{VAR{=}F} \limp S\_\textcolor{darkgreen}{EXT{=}NO} \\
      C_{aime_5} &: NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}T} \limp NP\_\textcolor{darkgold}{NUM{=}PL}\_\textcolor{darkgreen}{VAR{=}F} \limp S\_\textcolor{darkgreen}{EXT{=}ROOT} \\
      C_{aime_6} &: NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}F} \limp NP\_\textcolor{darkgold}{NUM{=}PL}\_\textcolor{darkgreen}{VAR{=}T} \limp S\_\textcolor{darkgreen}{EXT{=}ROOT}
  \end{align*}

  \end{small}
\end{frame}

@@

  \begin{columns}[c]
    \begin{column}{0.5\textwidth}
      \begin{center}
        \includegraphics[height=0.7\textheight]{../diagrams/constr-fail-1.pdf}
      \end{center}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{center}
        \includegraphics[height=0.7\textheight]{../diagrams/constr-fail-2.pdf}
      \end{center}
    \end{column}
  \end{columns}
\end{frame}

@@

>>>>

\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Outline}
    \tableofcontents[currentsection]
    \addtocounter{framenumber}{-1}
  \end{frame}
}

\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}
  {\hfill {\normalsize \insertframenumber{}/\inserttotalframenumber{}}}

@@

\frame{\titlepage \setcounter{framenumber}{1}}

@@

  \begin{columns}[c]
    \begin{column}{0.25\textwidth}
      {\small Syntax-semantics interface deals with syntactic
        constraints.}

      $\implies$ Complex.
    \end{column}
    \begin{column}{0.25\textwidth}
      \begin{center}
        \includegraphics[height=0.7\textheight]{../diagrams/fail1.pdf}
      \end{center}
    \end{column}
    \begin{column}{0.25\textwidth}
      {\small Syntactic constraints deal with the syntax-semantics
        interface.}

      $\implies$ Complex.
    \end{column}
    \begin{column}{0.25\textwidth}
      \begin{center}
        \includegraphics[height=0.7\textheight]{../diagrams/fail2.pdf}
      \end{center}
    \end{column}
  \end{columns}
\end{frame}

@@

  \begin{columns}[c]
    \begin{column}{0.25\textwidth}
      Second constraint reimplements first constraint.

      $\implies$ Pointless.
    \end{column}
    \begin{column}{0.25\textwidth}
      \begin{center}
        \includegraphics[height=0.7\textheight]{../diagrams/constr-fail-1.pdf}
      \end{center}
    \end{column}
    \begin{column}{0.25\textwidth}
      Third constraint reimplements first and second constraint.

      $\implies$ Pointless.
    \end{column}
    \begin{column}{0.25\textwidth}
      \begin{center}
        \includegraphics[height=0.7\textheight]{../diagrams/constr-fail-2.pdf}
      \end{center}
    \end{column}
  \end{columns}
\end{frame}

@@

\appendix
\newcounter{finalframe}
\setcounter{finalframe}{\value{framenumber}}

  Combined:
  \begin{small}
  \begin{align*}
      C_{aime_1} &: NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}F} \limp NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}F} \limp S\_\textcolor{darkgreen}{EXT{=}NO} \\
      C_{aime_2} &: NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}T} \limp NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}F} \limp S\_\textcolor{darkgreen}{EXT{=}ROOT} \\
      C_{aime_3} &: NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}F} \limp NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}T} \limp S\_\textcolor{darkgreen}{EXT{=}ROOT} \\
      C_{aime_4} &: NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}F} \limp NP\_\textcolor{darkgold}{NUM{=}PL}\_\textcolor{darkgreen}{VAR{=}F} \limp S\_\textcolor{darkgreen}{EXT{=}NO} \\
      C_{aime_5} &: NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}T} \limp NP\_\textcolor{darkgold}{NUM{=}PL}\_\textcolor{darkgreen}{VAR{=}F} \limp S\_\textcolor{darkgreen}{EXT{=}ROOT} \\
      C_{aime_6} &: NP\_\textcolor{darkgold}{NUM{=}SG}\_\textcolor{darkgreen}{VAR{=}F} \limp NP\_\textcolor{darkgold}{NUM{=}PL}\_\textcolor{darkgreen}{VAR{=}T} \limp S\_\textcolor{darkgreen}{EXT{=}ROOT}
  \end{align*}
  \end{small}
\end{frame}

\setcounter{framenumber}{\value{finalframe}}
